\input{preambule}

\begin{document}

\section{Preorders}

Let $\alpha$ be a set. We consider the maps $\LS$ and $\PLS$ from the $\Pre(s)$ of preorders on $\alpha$ to the powerset of the powerset of $\alpha$, sending a preorder $s$ to the set
of its nonempty lower sets (resp nonempty proper lower sets), and the map $\SL$ from the powerset of the powerset of $\alpha$ to $\Pre(\alpha)$ sending a set of subsets $E$ of $\alpha$ to 
the preorder $s$ defined by: "$a \le_s b$ if anf only if, for every $\beta\in E$, we have $b\in\beta \Ra a \in\beta$".

We have, for $s\in\Pre(\alpha)$ and $E$ a set of subsets of $\alpha$:
\begin{enumerate}
\item $s=SL(LS(s))$;
\item $E\subset LS(SL(E))$;
\end{enumerate}
Also, if $s$ is total and essentially locally finite, then every ideal of $s$ is principal, and we have $E\cup\{\top\}=LS(s)$ for every $E$ such that $s=SL(E)$.

We are mostly interested in the case where $s$ is total. Then $LS(s)$ (resp. $PLS(s)$) is the set of ideals (resp. proper ideals) of $s$. Also, both these sets are totally ordered by inclusion.
Indeed, let $\beta,\gamma\in PLS(s)$, and suppose that $\beta\not\subset\gamma$. Choose $a\in\beta$ such that $a\not\in\gamma$. If $b\in\gamma$, we cannot have $a\le b$ (otherwise $a$ would be in
$\gamma$, as $\gamma$ is a lower set for $s$), so $b\le a$, which implies that $b\in\beta$; so $\gamma\subset\beta$. 

Conversely, if $E$ is totally ordered by inclusion, then the preorder $s=SL(E)$ is total. Indeed, let $a,b\in\alpha$, and suppose that $a\not\le b$. Then there exists
$\beta\in E$ such that $b\in\beta$ and $a\not\in\beta$. If $\gamma\in E$ and $a\in\gamma$, we cannot have $\gamma\subset\beta$ because $a\not\in\beta$, so $\beta\subset\gamma$,
so $b\in\gamma$; this implies that $b \le a$. 

We want to investigate the link because $E$ being totally ordered by inclusion and locally finite, and $s$ being total and essentially locally finite. What I think holds:
\begin{enumerate}
\item If $s$ is total and essentially locally finite, then $LS(s)$ is total and locally finite, and isomorphic as a partial order to the quotient partial order of $s$ or that
quotient partial with a biggest element added, depending on whether $\alpha$ has no maximal element or has one.

\item If $E$ is totally ordered by inclusion and locally finite, and if, for every $a\in\alpha$, there exists an element of $E$ containing $a$, then $s$ is total and essentially
locally finite. The extra condition is necessary: if $\alpha=\Nat\cup{\infty}$ and $s$ is the usual order on it (i.e. it makes $\infty$ biggest than everything else), and if 
$E=\{[0,n],\ n\in\Nat\}$, then $s=SL(E)$, but $E$ is locally finite and $s$ is not.

\end{enumerate}

Can we similary characterize the (total?) preorders that have a finite number of finite blocks and at most one infinite block, which is maximal? This would mean that $s$ is 
essentially locally finite and every proper ideal is finite. So on $E$, it means that $E$ is totally ordered by inclusion and every proper element of $E$ is finite and $E$ itself
is finite; if we have these conditions, then it implies that $s=SL(E)$ is total essentially locally finite, then that proper initial intervals of $s$ are finite, so the blocks of $s$
are finite except maybe for the last one; also, there is a finite number of blocks because $E$ is finite.


\section{Ideals in the face complex of an abstract simplicial complex (and shellability)}

Let $K$ be an abstract simplicial complex on a set $V$. We say that $K$ is \emph{bounded} if it admits no strictly increasing infinite sequence of faces; this holds for example if the dimension
of the faces of $K$ is bounded. We denote by $V_K\subset V$ the set of vertices of $K$.

Facts:
\begin{enumerate}
\item Every filter of $K$ is principal (because it has minimal elements, as initial intervals are finite).
\item Ideals of $K$ correspond to nonempty subsets $S$ of $V_K$ with the property that every finite nonempty subset of $S$ is a face of $K$.
\item If $K$ is bounded, every ideal of $K$ is principal, and the maximal ideals are exactly the ones generated by facets.
\item In fact, the condition that $K$ is bounded is equivalent to the condition that every ideal is principal.
\item Prime ideals: these are ideals $I$ such that, for all $a,b$ not in $I$, there exists $c$ not in $I$ such that $c\leq a$ and $c\leq b$. For a simplicial complex,
this means that, for all $a,b$ not in $I$, the intersection $a\cap b$ is a face (or equivalently nonempty) and not in $I$. Suppose that $I$ corresponds to a set of vertices $S$,
vertices of $K$ except exactly one. Note that does not define an ideal in general, since it requires every finite subset of $S$ to be a face.
then $I$ being prime implies that $S$ contains all but at most one of the vertices of $K$; since prime ideals are proper, it is equivalent to the fact that $I$ contains all the

\end{enumerate}

We are interested in the following case: $\alpha=\Nat$ with its usual order, we consider the set of total preorders on $s$ that have a finite number of finite blocks and at most one infinite block, 
which is maximal. We take to be the image of this set by $PLS$ (minus the empty set, which corresponds to the trivial preorder), then $K$ is an abtract simplicial set on the powerset of $\Nat$.
Its vertices correspond to finite subsets of $\Nat$, it has no facets. Actually we don't need $\alpha$ to be $\Nat$, it could be any set. It is empty if $\alpha$ is empty or a singleton, and if $\alpha$
is finite of cardinality at least $2$ then $K$ is pure of dimension $\card(\alpha)-2$; if $\alpha$ is infinite then $K$ has no facets.

What are the ideals/maximal ideals of $K$? We suppose that $\alpha$ is infinite, otehrwise any ideal is principal. Then we have the principal ideals, but none of them is maximal. In general, the set
of vertices corresponding to an ideal will be a set of proper finite subsets of $E$ that is totally ordered by inclusion. It will be maximal if it contains an element of cardinality $n$ for every
positive integer $n$. Then the corresponding total preorder will be $\omega$ followed by one block containing an equivalence class of biggest element; this last block can be empty, though only if 
$\alpha$ is countable of course. 

\end{document}