\section{The face poset of an abstract simplicial complex}

We fix a set $\alpha$ and an abstract simplicial complex $K$ on $\alpha$.

\subsection{Definitions}

\begin{subdefi}[FacePoset] 
The \emph{face poset} of $K$ is the set of faces of $K$, partially ordered by inclusion.

\end{subdefi}

\begin{sublemma}[FacePosetIic\_is\_finite]
For every face $s$ of $K$< the half-infinite interval $]\leftarrow,s]$ is finite.

\end{sublemma}

\begin{sublemma}[FacePosetIcc\_is\_finite]
For all faces $s$ and $t$, the closed interval $[s,t]$ is finite.

\end{sublemma}

\begin{subdefi}[FacePosetLFB]
A structure of locally finite order with smallest element on the face poset of $K$.

\end{subdefi}

\begin{subdefi}[FacePosetLF]
A structure of locally finite order on the face poset of $K$.

\end{subdefi}

\subsection{Filters of the face poset}

\begin{sublemma}[FacePoset.Filters]
Every filter of the face poset if principal.

\end{sublemma}


\subsection{Ideals of the face poset}

\begin{subdefi}[SupportIdeal]
If $I$ is an ideal of the face poset, its \emph{support} is the union of all its members.

\end{subdefi}

\begin{subdefi}[IdealFromSet]
If $S$ a subset of $\alpha$, the subset of the face poset that it defines is the set of faces contained in $S$.

\end{subdefi}

\begin{sublemma}[SupportIdeal\_def]
Let $I$ be an ideal of the face poset. An element $a$ of $\alpha$ is in the support of $I$ if and only if there exists
a face $s$ of $K$ such that $s\in I$ and $a\in s$.

\end{sublemma}

\begin{sublemma}SupportIdeal\_eq
Let $I$ be an ideal of the face poset. An element $a$ of $\alpha$ is in the support of $I$ if and only if the face
$\{a\}$ of $K$ is an element of $I$.

\end{sublemma}

\begin{sublemma}[SupportIdeal\_contains\_faces]
Let $I$ be an ideal of the face poset. If $s$ is a face of $K$ such that $s\in I$, then $s$ is contained in the support of $I$.

\end{sublemma}

\begin{sublemma}[SupportIdeal\_monotone]
If $I,J$ are ideals of the face poset of $K$ such that $I\subset J$, then the support of $I$ is contained in the support of $J$.

\end{sublemma}

\begin{sublemma}[SupportIdeal\_nonempty]
If $I$ is an ideal of the face poset of $K$, then the support of $I$ is nonempty. (Note that ideals are nonempty by definition.)

\end{sublemma}

\begin{sublemma}[Finset\_SupportIdeal\_aux and Finset\_SupportIdeal]
Let $I$ be an ideal of the face poset of $K$. Then any nonempty finite subset of the support of $I$ is a face of $K$.

\end{sublemma}

\begin{sublemma}[MemIdeal\_iff\_subset\_SupportIdeal]
Let $I$ be an ideal of the face poset of $K$ and $s$ be a face of $K$. Then $s\in I$ if and only if $s$ is contained in the
support of $I$.

\end{sublemma}

\begin{sublemma}[SupportIdeal\_principalIdeal]
Let $s$ be a face of $K$. The support of the principal ideal generated by $s$ is equal to $s$.

\end{sublemma}

\begin{sublemma}[SupportIdeal\_top]
Let $I$ be an ideal of the face poset of $K$. If $I$ is equal to the set of all faces of $K$, then the support of $I$
is equal to the set of vertices of $K$.

\end{sublemma}

\begin{sublemma}[IdealFromSet\_only\_depends\_on\_vertices]
Let $S$ be a subset of $\alpha$. Then $S$ and its intersection with the set of vertices of $K$ define the same subset
of the face poset of $K$.

\end{sublemma}

\begin{sublemma}[IdealFromSet.IsLowerSet]
Let $S$ be a subset of $\alpha$. The subset of the face poset of $K$ that it defines is a lower set.

\end{sublemma}

\begin{sublemma}[IdealFromSupport]
Let $I$ be an ideal of the face poset of $K$. Then $I$ is equal to the subset defined by its support.

\end{sublemma}

\begin{sublemma}[IdealFromSet\_DirectedOn\_iff\_aux \& IdealFromSet\_DirectedOn\_iff]
Let $S$ be a subset of $\alpha$ contained in the set of vertices of $K$. Then the subset of faces defined by $S$ is
directed if and only every nonempty finite subset of $S$ is a face of $K$.

\end{sublemma}

\begin{sublemma}[PrincipalIdeal\_iff]
An ideal of the face poset of $K$ is principal if and only if its support is finite.

\end{sublemma}

\begin{sublemma}[Subideal\_of\_Principal\_is\_Principal]
If $I,J$ are ideals of the face poset of $K$ such that $I\subset J$ and $J$ is principal, then $I$ is principal.

\end{sublemma}

\begin{sublemma}[AllIdealsPrincipal\_iff\_AllMaximalNonProperIdealsPrincipal]
The following are equivalent:
\begin{enumerate}
\item Every ideal of the face poset of $K$ is principal.
\item Every nonproper maximal ideal of the face poset of $K$ is principal.


\end{enumerate}
\end{sublemma}

\begin{sublemma}[Facet\_iff\_principal\_ideal\_maximal]
Let $s$ be a face of $K$. Then $s$ is a facet if and only if the principal ideal that it generates is nonproper maximal.

\end{sublemma}

\begin{sublemma}[Top\_ideal\_iff\_simplex]
The following are equivalent:
\begin{enumerate}
\item The set of all faces of $K$ is an ideal.
\item Every nonempty finite subset of the set of vertices of $K$ is a face of $K$.

\end{enumerate}
\end{sublemma}


\subsection{Noetherianity of the face poset}

\begin{sublemma}[Noetherian\_implies\_every\_face\_contained\_in\_facet]
If the face poset of $K$ is Noetherian, then every face of $K$ is contained in a facet.

\end{sublemma}

\begin{sublemma}[Noetherian\_nonempty\_implies\_facets\_exist]
If the face poset of $K$ is Noetherian and $K$ is nonempty, then $K$ has a facet. 

\end{sublemma}

\begin{sublemma}[Finite\_dimensional\_implies\_Noetherian]
If the dimension of $K$ is finite, then the face poset of $K$ is Noetherian.

\end{sublemma}

\begin{sublemma}[Finite\_implies\_Noetherian]
If $K$ is a finite complex, then its face poset is Noetherian.

\end{sublemma}

\begin{sublemma}[Finite\_implies\_finite\_dimensional]
If $K$ is a finite complex, then its dimension is finite.

\end{sublemma}

\begin{sublemma}[Dimension\_of\_Noetherian\_pure]
If the face poset of $K$ is Noetherian and all facets of $K$ have the same cardinality, then $K$ is pure.

\end{sublemma}
